---
title: "Assignment_B1"
author: "Mathias Delhaye"
date: "02/11/2021"
output: github_document
---

# Loading the needed packages

```{r}
library(tidyverse)
library(testthat)
library(gapminder)
library(ggplot2)
library(datateachr)
library(palmerpenguins)
``` 

# Building the function

```{r}
#' @title Counting iteration
#' 
#' @description This function count the number of iteration for the different possibilities of one variable of a table
#' 
#' @params data is a table
#' @params x is the name of the variable for which we want to count the number of iteration for the different possibilities
#' 
#' @return a plot of columns in the decreasing order, showing the counts for every possibilities of the variable of interest
#' 
#' @examples
#' counting_iteration(vancouver_trees, neighbourhood_name), to count the iteration of each neighbourhood in the dataset vancouver_trees
#' counting_iteration(penguins, species) to count the iteration of each specie in the dataset penguins
#' counting_iteration(starwars, homeworld) to count the iteration of each homeworld in the dataset starwars

counting_iteration <- function (data, x) {
  data%>%
    group_by({{x}})%>%
    summarise(n=n())%>%
    drop_na()%>%
    mutate({{x}} := fct_reorder({{x}}, n))%>%
    ggplot(aes({{x}}, n))+
    geom_col()+
    coord_flip()
}
```

# Examples

```{r}
counting_iteration(vancouver_trees, neighbourhood_name)
```

Here we used the data set *vancouver_trees* and look for the number of trees planted in each neighborhood for the studied period. 

```{r}
counting_iteration(penguins, species)
```

Here we used the data set *penguins* from the library **palmerpenguins**, and look at the number of penguins for each specie. 

```{r}
counting_iteration(starwars, homeworld)
```

Here we used the data set *starwars* to look at the number of character coming from each world. 


# Testing the function

```{r}
test_that("counting_iteration function", {
  expect_equal(
        as.character(rlang::get_expr(counting_iteration(vancouver_trees, neighbourhood_name)$mapping$y)), "n") #checking the name of the y axis
  expect_equal(
    as.character(rlang::get_expr(counting_iteration(vancouver_trees, neighbourhood_name)$mapping$x)), "neighbourhood_name"
  ) #checking the name of the y axis
  expect_error(counting_iteration(gapminder, year)) #the function does not work with a variable containing numerical value
  expect_true(
        "GeomCol" %in% class(counting_iteration(vancouver_trees, neighbourhood_name)$layers[[1]]$geom)) #the class of the plot should be GeomCol
})
```